---
title: "Gun Control Chi Square"
author: "Geoffrey Cook"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here is some fun text for you to read. 

Here is more stuff for you to read. No peaking! gotta wait until I push to Git.

Ha Ha Ha... >.>

```{r}
library(tidyverse)
```

Here is another thing for you to read!

It works!!! :) 
#########################################

Creator (Geoff)
Getting the gc_df.csv data, loading tidyverse, and getting some summary counts

```{r}
gc_df <- read_csv("gc_df.csv")

get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>%  #allows you to use the key value pair to convert levels that exist in one column to another column
  select(-gender)

rownames(get_guns) <- c("Female", "Male")
```

I am the Collaborator (Alex) and I am going to do chi-square.

Is there a significant difference in gun control perspectives (as related to access to guns) for males and females?

Is there a significant association between sex and gun control recommendations?

Is perception of gun control access independent of sex?

Chi-Square

```{r}

guns_prop <- prop.table(as.matrix(get_guns), 1)
guns_prop

# Perform chi-square

guns_x2 <- chisq.test(get_guns)
guns_x2

```

Recommended gvmt action on gun access differs significantly for males and females ($\chi^2$(`r guns_x2$parameter`) = ...., p < 0.001)
